\chapter*{General Conclusion}

The development of the \textbf{AgriGov Market} platform represents a strategic response to the pressing need for digital transformation within the Algerian agricultural sector. Throughout this work, we have addressed the critical challenges of market opacity, over-intermediation, and logistical inefficiencies that have long hindered the coordination between farmers, transporters, and buyers. By placing this digital ecosystem under the official supervision of the Ministry of Agriculture, we have proposed a solution that not only facilitates direct trade but also empowers the state with the tools necessary for effective market regulation and food security monitoring \cite{Chetibietal2026}.

Our journey began with a rigorous \textbf{Needs Analysis}, where we identified the specific requirements of each stakeholder. This phase allowed us to move beyond a general understanding of the problem to a precise definition of the system's functional boundaries through UML modeling. Subsequently, in the \textbf{System Design} phase, we translated these requirements into a technical blueprint. The creation of a structured database schema, a detailed class architecture, and a modern technology stack has resulted in a platform that is both robust and scalable, capable of managing the real-time complexities of national agricultural logistics \cite{Belhadi2024}.

The \textbf{AgriGov Market} platform achieves its primary goal: bridging the gap between traditional agricultural practices and modern digital efficiency. While the current implementation provides a solid and deployable foundation for direct trade and state regulation, several meaningful extensions have been identified for future development:

\begin{itemize}
	
	\item \textbf{IoT-Based Cargo Monitoring:} integrating sensors into transport vehicles to track temperature, humidity, and location in real time, ensuring product quality throughout the delivery chain — particularly critical for perishable goods.
	
	\item \textbf{AI-Driven Price Prediction:} training predictive models on historical transaction data to help the Ministry anticipate market imbalances, seasonal price spikes, and supply shortages before they escalate \cite{Seltetal2026}.

	\item \textbf{Blockchain Traceability:} recording each product's journey — from origin farm to final buyer — on an immutable ledger, reinforcing food safety guarantees and building consumer confidence in the platform.
	
\end{itemize}

Ultimately, this project serves as a pilot model for how information technology can be leveraged to modernize strategic sectors and support sustainable economic growth in Algeria. The modular architecture built throughout this work ensures that these enhancements can be adopted progressively, allowing the platform to evolve alongside the needs of the agricultural sector without compromising the stability of what has already been delivered.