\chapter*{General Introduction}

The digitalization of agriculture has become a global necessity for modernizing food systems and ensuring economic stability in an increasingly dynamic world. In Algeria, this transformation is considered a national priority led by the Ministry of Agriculture, aiming to strengthen food security, enhance market transparency, and improve farmers’ incomes \cite{Chetibietal2026}. Despite these efforts, the agricultural sector continues to face several major challenges, including limited direct access to buyers, the absence of reliable pricing information, inefficient logistics, and weak coordination between producers and transporters \cite{Seltetal2026}.

To overcome these limitations, this project proposes AgriGov Market, a national web-based platform designed to connect farmers, buyers, and transporters under official supervision. The system facilitates direct transactions, ensures pricing transparency, and organizes the delivery process of agricultural products. In doing so, it helps bridge the gap between different market actors while providing the Ministry with an effective tool for monitoring and regulating the agricultural market \cite{Mohammadetal2025}.

This thesis is organized into two main chapters:

\begin{itemize}
	\item \textbf{Chapter 1: Needs Analysis} \\
	This chapter defines the project context and presents the problem statement. It identifies the main actors involved in the system and describes their roles. Additionally, it includes use case diagrams and system sequence diagrams to specify the functional requirements, such as product management, order processing, and delivery tracking.
	
	\item \textbf{Chapter 2: System Design} \\
	This chapter focuses on transforming the identified requirements into a concrete technical solution. It presents class diagrams, the overall activity flow, and the relational database schema. Furthermore, it describes the system architecture and the technologies selected for implementation.
\end{itemize}

Together, these chapters provide a comprehensive view of the development process behind the AgriGov Market platform \cite{benzadri2025}.